---
title: "Simple Linear Regression"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---

```{r, message=FALSE, warning=FALSE}
# Load your libraries
library(car)
library(tidyverse)
library(readr)
library(pander)
# Load your data after saving a csv file in your Data folder.
# You can use either 
#   someName <- read.csv("../Data/YourDataFileName.csv", header=TRUE)
# or
#   library(readr)
#   someName <- read_csv("../Data/YourDataFileName.csv")

# Don't forget to run "Session -> Set Working Directory -> To Source file location"

steps_to_calories <- read_csv("../../linear_regression_data.csv")
```


<!-- Directions

Come up with a simple linear regression of your own creation. 

* Write the Background and clearly state your question. Then collect data and perform the linear regression analysis in order to answer your question. Use the proper order of first, ask the question, then second, figure out the answer.

* You should collect both the quantitative response variable and the quantitative explanatory variable yourself. This can be data you collect from 
    - the internet (like weather data, Facebook data, or sports data) 
    - your own experiment 
    - your own observational study
* However,     
    - The data should not be a single pre-existing dataset. It must be something that you piece together yourself.

* You need at least $n=3$ $(X,Y)$ pairs to perform the regression. However, your regression will only be useful if you can get around $n=10$ or more observations.

-->


## Background

I collected walking data off of my google fit app. This app tracks my steps and how many calories I burn through the day walking. I put this data in a CSV file and will do a linear regression analyses to see if there is a relationship between amount of steps taken and the amount of calories I burn.

## Question and Hypotheses:

* Is there a linear relationship between steps walked and calories burned?

* Null Hypotheses : the slope is equal to 0.
* Alternative Hypotheses : the slope is not equal to 0.


## Analysis

```{r, warning=FALSE}
steps_lm <- lm(calories_burned ~ steps_walked, data = steps_to_calories)
summary(steps_lm) %>% pander()

par(mfrow=c(1,3))
plot(steps_lm, which=1:2)
plot(steps_lm$residuals, main = "Residuals vs Order", xlab = "", ylab = "Residuals")
```

The simple linear regression analyses is a good test for this because:

1) There seems to be a linear relationship. 
2) The error terms seem to be normaly distributed.
3) The variance is constant.
4) The x values are measured and fixed without error.
5) The error terms are independent.

These 5 points can be checked with the residuals and the Q-Q plot.
 
We will use an alpha of 0.05 with this test. The P values are lower than this so we will reject the null. 

## Graph

```{r, warning=FALSE}

ggplot(data = steps_to_calories) +
  geom_point(mapping = aes(x = steps_walked, y = calories_burned, color = "orangered3")) +
  geom_smooth(method = lm, se = FALSE, mapping = aes(x = steps_walked, y = calories_burned)) +
  labs(title = "Steps Walked vs Calories Burned", x = "steps walked", y = "calories burned") +
  theme(plot.title = element_text(hjust = 0.5),
        legend.position = "none")

```

The graph shows a very strong positive linear relationship between steps walked and calories burned

## Interpretation

The slope is 1.346 and the r-squared value is 0.8573 which shows a strong positive linear relationship between steps walked and calories burned.

## Conclusion

There is a positive strong linear relationship between steps walked and calories burned. We can reject the null hypotheses.







