---
title: "My Simple Logistic Regression"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---

<!-- Find some data of interest to you that can be analyzed with a logistic regression. Complete your Logistic Regression Analysis using this file. 

Hint, run the command 

> data() 

in your Console to see available datasets in R that you could use for this Analysis. You are also welcome to collect data yourself, or find other available datasets online for this Analysis. Just be careful to not use anyone else's "analysis" for this Analysis. Also, no conducting surveys unless you have IRB approval to do so. -->

```{r, include=FALSE}
library(mosaic)
library(ResourceSelection) 
library(readr)
library(tidyverse)
library(pander)
```

```{r warning=FALSE, include=FALSE}

employment <- read_csv("../../Data/mental_illness_employment.csv")


fact_level <- c("Some highschool", "High School or GED", "Some Undergraduate", "Completed Undergraduate", "Some Masters", "Completed Masters", "Some Phd", "Completed Phd")
employment <- employment %>% 
  mutate(Education = factor(Education, levels = fact_level)) %>% 
  mutate(EducationLevel = case_when(Education == "Some highschool" ~ 1,
                            Education == "High School or GED" ~ 2,
                            Education == "Some Undergraduate" ~ 3,
                            Education == "Completed Undergraduate" ~ 4,
                            Education == "Completed Masters" ~ 5,
                            Education == "Some Phd" ~ 6,
                            Education == "Completed Phd" ~ 7,))
 
```

### Background

I will use logistic regression to try to predict mental illness based off of education level. Here is the logistic regression model:

$$
  P(Y_i = 1|\, x_i) = \frac{e^{\beta_0 + \beta_1 x_i}}{1+e^{\beta_0 + \beta_1 x_i}} = \pi_i
$$

where for observation $i$: 

* $Y_i = 1$ denotes that at least one education level predicts a mental illness, 
* $Y_i=0$ denotes no education level predicts a metal illness, and 
* $x_i$ denotes the specific education level being tested.

### Questions and Hypotheses

Question: Is education level a good predictor of mental illness?

Hypotheses: We will use the Deviance Goodness of Fit Test because there are replicated values of each $x_i$

$$
  H_0: \pi_i = \frac{e^{\beta_0 + \beta_1 x_i}}{1+e^{\beta_0 + \beta_1 x_i}}
$$
$$
  H_a: \pi_i \neq \frac{e^{\beta_0 + \beta_1 x_i}}{1+e^{\beta_0 + \beta_1 x_i}}
$$


### Analysis

Here is a logistic regression test:

```{r, warning=FALSE}
mental_glm <- glm(mental_illness ~ EducationLevel, data = employment, family = binomial)
summary(mental_glm) %>% pander()

```

##### I will use an alpha of 0.05:

Here we see that education level p-value is above 0.05 so it isn't a good indication that it affects the probability of mental illness. 


I will use the Deviance Goodness of Fit Test in order to determine if logistic regression is a good test to use because there are many repeated x-values.

Here is the value for the goodness of fit test:
```{r, warning=FALSE}
pander(pchisq(354.0, 320, lower.tail = FALSE))
```

This value is above 0.05 remember that the null hypothesis was that logistic regression would be a good fit for the data so we can conclude the null.


### Graphical Summary

```{r, warning=FALSE}

ggplot(data = employment, mapping = aes(x = EducationLevel, y = mental_illness)) +
  geom_point(mapping = aes(color = Education)) +
  geom_smooth(method = "glm", method.args = list(family = "binomial"), se = FALSE) +
  labs(x = "Education Level", y = "Probability of Mental Illness", title = "Education Level is Not a Good Predictor of Mental Illness") +
  theme(legend.position = "bottom", plot.title = element_text(hjust = 0.5))
  
```

* Here we see the probabilities graphically. But we shouldn't trust this beause our p-value for education level was too high. The logistic fit is good though.


### Interpretation

It seems like the education level of an individual is not a good indication of their mental health. There are probably some other variables that would be better to look at.



