---
title: "High School Seniors t Test"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
library(DT)
library(pander)
library(readr)
library(car)
library(lattice)
```

```{r, message=FALSE, warning=FALSE}

HSS <- read_csv("../../Data/HighSchoolSeniors.csv")
HSS2 <- HSS %>% 
  drop_na() %>% 
  filter(Handed == "Right-Handed" | Handed == "Left-Handed")
#Remember: select "Session, Set Working Directory, To Source File Location", and then play this R-chunk into your console to read the HSS data into R. 
```

<!-- Instructions

1. Use the HSS dataset in R to come up with a question that can be answered with a t Test. 

Here is a link to the survey given to the students that participated in the study:
https://ww2.amstat.org/censusatschool/pdfs/C@SQuestionnaire.pdf
(Use the link to learn about what each column of data in the data set represents.)

2. Establish why your question is interesting and rephrase the question using a statistical "null" and "alternative" hypothesis. (Hint, see the "Math 325 Notebook -> R Help -> R-Markdown Hints" page of your textbook for instructions on how to write mathematical hypotheses.)

3. Clearly answer your question using statistics. Be sure to compute a p-value and provide supporting numerical and graphical summaries.

Note: you can create "groups" from the data in many ways. For example, suppose you wanted to create a variable that grouped people according to whether they thought recycling was more important than conserving water. You could do this by:

```{r}
HSS <- HSS %>%
  mutate(recycling_than_water = ifelse(Importance_recycling_rubbish >	Importance_conserving_water, "Recycling More Important", "Water Conservation More Important"))
```

-->


## Background

I have data from a High School dataset and I want to do an independent sample t-test to see if left handed people have a higher average score in a memory game versus right handed people.


## Questions and Hypotheses

question : Do left handed people have a higher average score in a memory game than right handed people?

* Defining variables: 
$$\mu_1 = \text{the mean memory score for left handed people}$$ 
$$\mu_2 = \text{the mean memory score for right handed people}$$ 

Hypotheses : 
$$H_0: \mu_1 - \mu_2 = 0$$

$$H_a: \mu_1 - \mu_2 > 0$$

## Analysis

```{r, warning=FALSE}

par(mfrow = c(1,2))
qqPlot(HSS2$Score_in_memory_game[HSS2$Handed=="Left-Handed"], ylab = "left handed")
qqPlot(HSS2$Score_in_memory_game[HSS2$Handed=="Right-Handed"], ylab = "right handed")


```
The some of the data for the right handed memory scores don't look normal but it's just a few data points compared to all the rest so we can keep doing our t-test.


```{r, warning=FALSE}
test <- t.test(HSS2$Score_in_memory_game[HSS2$Handed=="Left-Handed"],
               HSS2$Score_in_memory_game[HSS2$Handed=="Right-Handed"],
       data = HSS2,
       mu = 0, 
       alternative = "greater", 
       conf.level = 0.95)

pander(test)

```

I'm going to use an alpha value of 0.05 here. I see that the p value is 0.4997 which is well above our alpha so it looks like we can reject the alternative hypothesis that left handed people have a highter average score in the memory game than right handed people.

## Graphical Summary

```{r, warning=FALSE}
xyplot(Score_in_memory_game ~ as_factor(Handed), data = HSS2, type=c("p","a"), main = "comparing means for the memory game", xlab = "Handedness", ylab = "Memory Game Score", sub = "the mean looks the same for both groups")

```

## Interpretation and Conclusion
Here we can see visually that the means look the relatively the same for both left and right handed people for the memory score. So according to this and our t-test there is no significant difference in the memory of left and right handed people.





















