---
title: "Stephanie's Housing Request"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
    toc: true
    toc_float: true
---

**Week 2 Analysis**

```{r, include=FALSE}
library(mosaic)
library(tidyverse)
library(pander)
library(DT)
library(tidyr)
library(ggplot2)
library(ggthemes)
library(ggrepel)
# If you get an error stating: 
            # Error in library(DT): there is no package called 'DT'
            # You will need to run: install.packages("DT") 
            # in your Console, then try "Knit HTML" again.
Rent <- read_csv("../Data/Rent.csv")
```


<br />

## Background

Stephanie[^1] is a student that will be starting school at BYU-Idaho next semester. Suppose she sent you the following email.

----

"Hi. My name is Stephanie. I would like to learn about what housing options I have for living at BYU-Idaho next semester. It will be my first semester there, so I would like to find something that is close to campus and around $300 a month in rent. I'm not too picky on roomates, but I would like somewhere that has a lot of people around so I can get to know as many people as possible. Thanks in advance!"

----

## Response

Dear Stephanie,

  Based off of your criteria I suggest you rent your apartment at Birch Plaza. I recommend it because it is the complex with the most amount of people that you can meet for the price that you wanted, and it is very close to campus being just a minute long walk away. Below I have a scatterplot graph that compares walking minutes to campus and price. Apartments that have the lowest walking minutes and the highest capacity are great candidates. These apartments will show up at the top left of the graph. In contrast the worst candidates will show up at the bottom right. I will also include a table that shows more specifics about each apartment including their phone number, address and exact price per semester. 



<!-- Hint, you should probably subset the Rent dataset to only show the "Approved Women's Housing" since Stephanie won't be interested in Male Housing options. Notice how this text in green doesn't show up in the HTML output because we used the HTML comment tags around this text. --> 

```{r, warning=FALSE}
# Code to get you started, be sure to use a subset of Rent instead of Rent in this code though.
# Wrangle the data
stephs_choice_rent <- Rent %>%
  filter(Gender == "F", Price <= 1200, Capacity >= 100, WalkingMinutes < 10)

```


```{r,warning=FALSE}
# Visualize the data
p = ggplot(data = stephs_choice_rent) +
  geom_point(aes(x = WalkingMinutes, y = Capacity, size = Capacity, color = Apartment, alpha = 0.9)) +
   geom_text_repel(data = stephs_choice_rent, aes(x = WalkingMinutes, y = Capacity, label = Apartment, colour = Apartment), show.legend = FALSE, nudge_x = -1,  nudge_y = -3) +
  labs(x = "Walking Minutes to Campus", y = "Total Apartment Capacity", title = "Walking Time vs Capacity", subtitle = "Bigger points correspond to higher capacity") +
  theme_bw() +
  theme(legend.position = "none")
p
# table for Stephanie that shows more specific info
stephs_table <- stephs_choice_rent %>%
  group_by(Apartment) %>%
  select(Apartment, Address, Phone, Price, Capacity) %>%
  pander(caption = "here is your table so you can see specifics")
stephs_table
```

## Conclusion
If Stephanie wants the best apartment she should go with Birch Plaza.

[^1]: Note that Stephanie is a fictional character who is based on real experiences of many faculty and staff here at BYU-Idaho.
