---
title: "Chocolate"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---

```{r, include=FALSE}
# Be sure to use your file menus at the top of R-Studio to:
# "Session -> Set working directory -> To source file location"
# Then play this chunk and the next one to get the data into R.
library(mosaic)
library(car)
library(DT)
library(pander)
library(readr)
library(tidyverse)
library(ggbeeswarm)
choc <- read_csv("../../Data/Chocolate.csv")
```

```{r, eval=FALSE}
View(choc)
```

----

<!-- Instructions:

 Use the Chocolate dataset and a Kruskal-Wallis Test(s) to answer an interesting question(s) that you come up with.
 
 About the dataset:
 
  * Company: Name of the company manufacturing the bar.

  * Orig: The specific geo-region of origin for the bar.

  * Review: Date of publication of the review.

  * Cocoa: Cocoa percentage (darkness) of the chocolate bar being reviewed.

  * Location: Manufacturer base country.

  * Rating: Expert rating for the bar.
      5= Elite (Transcending beyond the ordinary limits)
      4= Premium (Superior flavor development, character and style)
      3= Satisfactory(3.0) to praiseworthy(3.75) (well made with special qualities)
      2= Disappointing (Passable but contains at least one significant flaw)
      1= Unpleasant (mostly unpalatable)

   * Type: The variety (breed) of cocoa bean used, if provided.
   
   * BroadOrig: The broad geo-region of origin for the bean.

Note this dataset and description come from: © 2018 Kaggle Inc for further details visit:

[Kaggle.com](https://www.kaggle.com/rtatman/chocolate-bar-ratings/data)


If you want to give your critiquers some ideas about what you have questions on and would like help with, place those details here.-->
**Comments to Critiquers:** 



<!--End your comments to your critiquers before this line.-->

----

<!--Begin writing your Analysis after this point.-->

## Background

I'm trying to find out which country between America, Hungary, France and Switzerland has the highest rated chocolate. I served my mission in Hungary so I want to see how it stacks up against some of the bigger chocolate bar producers.

## Question and hypothesis

Question: Which country between America, Hungary, France and Switzerland has the highest rated choclolate?

* Null Hypothesis: All samples are from the same distribution.

* Alternative Hypothesis: At least one sample's distribution is stochastically different.

## Analysis

```{r, warning=FALSE}

choc_filtered <- choc %>% filter(Location %in% c("U.S.A.", "Hungary", "France", "Switzerland"))
pander(kruskal.test(Rating ~ Location, data = choc_filtered))
```

Here we'll use an alpha of 0.05 

Based off of our P-value being less than 0.05 as calculated with the Kruskal-Wallis test we can reject our null hypotesis. We can accept that at least one sample's distribution is stochastically different.

## Graphical Summary
  
```{r, warning = FALSE}
ggplot(data = choc_filtered, aes(x = Location, y = Rating, fill = Location)) +
  geom_boxplot() +
  labs(title = "Very little difference in the medians")

```

Based off of the box plot we can't tell a whole lot about which chocolate is the best and we can see that the median is pretty much the same for all the countries.

```{r, warning = FALSE}
choc_filtered %>%
  group_by(Location) %>%
  summarise(average = mean(Rating)) %>%
  pander()
  

```

To get a closer look I found the average rating for all the chocolates in the countries and found that Switzerland had the highest average out of all of them with my mission country of Hungary coming in third place.


## Interpretation

Based of of this test and the means I found that the highest average scoring chocolate is made by Switzerland. Well they are famous for their chocolates after all. My mission country of Hungary didn't do so badly compared to the other countries and was ahead of the United States.










