---
title: "Day Care Fines"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---

<script type="text/javascript">
 function showhide(id) {
    var e = document.getElementById(id);
    e.style.display = (e.style.display == 'block') ? 'none' : 'block';
 }
</script>

```{r, include=FALSE}
library(mosaic)
library(DT)
library(pander)
library(car)
library(tidyverse)

# To get the "late" dataset into your R Console, 
# you need to go to your file menu of R-Studio and select
# "Session, Set working directory, To source file location"
# Then click the green "play" arrow in 
# the top right corner of this gray R-Chunk. 
late <- read.csv("../../Data/late.csv", header=TRUE)
# Then type:
# > View(late)
# in your R Console
```



----

<!--If you want to give your critiquers some ideas about what you have questions on and would like help with, place those details here.-->

**Comments to Critiquers:** 



<!--End your comments to your critiquers before this line.-->

----


## Background {.tabset .tabset-fade}

### Overview
<!-- Be sure to add your own background here before beginning the Analysis. -->
Here we have private daycares and we want to know if instituting a fine will reduce the amount of children that get picked up late by their parents.

## Hypothesis

##### First question and pair of hypothesis:
1. Is there a difference between the control group and the fined group?
- null hypothesis: There is no difference between the groups

- alternative hupothesis: There is a difference between the groups

##### Second question and pair of hypothesis:
2. Is there a difference between the weeks for the number of childeren that have been picked up late?
- null hypothesis: There is no difference between the weeks for the number of childeren that have been picked up late

- alternative hypothesis: There is a difference between the weeks for the number of childeren that have been picked up late

##### Third question and pair of hypothesis:
3. Is there a difference between the amount of late children before the fine, during the fine and after the fine?
- null hypothesis: There is no difference in the amount of late children between weeks where the fine is introduced, during the fine period and after the fine period.

- alternative hypothesis: There is a difference in the amount of late children between weeks where the fine is introduced, during the fine period and after the fine period.



<!--End your background before here.-->
<!--Click the little black arrow to 
the left to expand/hide these next sections.-->
### Study Details

<div style="color:#a8a8a8;">
This background is quoted directly from the article ["A Fine is a Price"](http://rady.ucsd.edu/faculty/directory/gneezy/pub/docs/fine.pdf). 
</div>

<div style="padding-left:30px; padding-right:30px;">

There are two types of day-care centers in Israel: private and public. A study was conducted in 10 private day-care centers in the city of Haifa from January to June 1998. All of these centers are located in the same part of town, and there is no important difference among them. During the day children are organized into groups according to age, from 1 to 4 years old. Each day-care center is allowed to hold a maximum of 35 children. In some exceptional cases a few additional children are allowed. The fee for each child is NIS 1,400 per month. (The NIS is the New Israeli Shekel.) At the time of the study, a U.S. dollar was worth approximately NIS 3.68, so the fee was about $380 at that time. 

The contract signed at the beginning of the year states that the day-care
center operates between 0730 and 1600. There is no mention of what happens if parents come late to pick up their children. In particular, before the beginning of the study, there was no fine for coming late. When parents did not come on time, one of the teachers had to wait with the children concerned. Teachers would rotate in this task, which is considered part of the job of a teacher, a fact that is clearly explained when a teacher is hired. Parents rarely came after 1630. 

A natural option [to fix the problem of parents showing up late] is to introduce a fine: every time a parent comes late, [they] will have to pay a fine. Will that reduce the number of parents who come late? If the fine is removed, will things revert back to the way they were originally?

The overall period of the study was 20 weeks. In the first 4 weeks we
simply recorded the number of parents who arrived late each week. At the
beginning of the fifth week, we introduced a fine in six of the 10 day-care centers, which had been selected randomly. The announcement of the fine was made with a note posted on the bulletin board of the day-care center. Parents tend to look at this board every day, since important announcements are posted there. The announcement specified that the fine would be NIS 10 for a delay of 10 minutes or more. The fine was per child; thus, if parents had two children in the center and they came late, they had to pay NIS 20. Payment was made to the principal of the day-care center at the end of the month. Since monthly payments are made to the owner during the year, the fines were added to those amounts. The money was paid to the owner, rather then to the teacher who was staying late (and did not get any additional money). The teachers were informed of the fine but not of the study. Registering the names of parents who came late was a common practice in any case.

At the beginning of the seventeenth week, the fine was removed with no explanation. Notice of the cancellation was posted on the board. If parents asked why the fines were removed, the principals were instructed to reply that the fine had been a trial for a limited time and that the results of this trial were now being evaluated.

A comparison with other fines in Israel may give an idea of the size of
the penalty that was introduced. A fine of NIS 10 is relatively small but not insignificant. In comparison, the fine for illegal parking is NIS 75; the fine for driving through a red light is NIS 1,000 plus penalties; the fine for not collecting the droppings of a dog is NIS 360. For many of these violations, however, detection and enforcement are low or, as in the case of dog dirt, nonexistent in practice. A baby-sitter earns between NIS 15 and NIS 20 per hour. The average gross salary per month in Israel at the time of the study was NIS 5,595.

</div>


### The Data (Wide)


The `late` Day Care Center data is shown here in the "wide data format". 

```{r, out.width=300}
#Show the full width of the "Wide" version of the late data:
pander(late, split.tables = Inf)
```


### The Data (Long)

The `Late` Day Care Center data is shown here in the "long data format".

```{r}
# This code reshapes the data into "long" format called Late.
# To get the "Late" dataset into your R Console, 
# you need to click the green "play" arrow in 
# the top right corner of this gray R-Chunk. 
# Then type:
#   > View(Late)
# in your R Console
Late <- reshape(late,
                varying = paste("Week",1:20, sep=""), 
                v.names = "No.ofLateChildren",
                timevar = "Week", 
                times = 1:20, 
                idvar = "Center",
                new.row.names = 1:200,
                direction = "long")
pander(Late)
```


 
##  
<!-- You can begin writing again after here.-->



## Analysis

```{r, warning=FALSE}

Late_week_groups <- Late %>% mutate(week_group = case_when(Week %in% c(1,2,3,4) ~ "before",
                                                           Week %in% c(5:16) ~ "during",
                                                           Week %in% c(17,18,19,20) ~ "after"))
  
between_control_treatment_week <- aov(No.ofLateChildren ~ as_factor(Treatment) + as_factor(week_group) + as_factor(Week) + as_factor(Treatment): as_factor(week_group), data = Late_week_groups)
pander(summary(between_control_treatment_week))
```

###### For this analysis an alpha of 0.05 will be used
It looks like we can reject the null hypothesis for all of our questions and accept the alternatives that there is a difference in the amount of late children among the control and fined groups, among the weeks, and among the different groups before the fine, during the fine and after the fine. To look at what exactly those differences are we can look at the graphs below that show further detail.

## Graphical Summary and Interpretations

```{r, warning=FALSE}
par(mfrow = c(1,2))
plot(between_control_treatment_week, which = 1:2)
```

This is just checking our residuals and the normality of the data which looks fine enough to do an ANOVA analysis.

```{r, warning=FALSE}

xyplot(No.ofLateChildren ~ Treatment, data = Late, type = c("p", "a"), main = "Significance of Fining", col = "blue")
```

Here we get some suprising results. We see that with a fine the amount of late children that are being picked up actually increases.

```{r, warning=FALSE}
xyplot(No.ofLateChildren ~ Week, data = Late, groups = Treatment, type = c("p", "a"), main = "child centers that are fined show more late children than the control", auto.key = list(corner = c(1,1)))
```

At first it seems like when the fine is initiated that the amount of late children goes down but notice the control group also goes down during week 5 to the same level. This leads me to believe that the fine didn't play a significant role for the drop in late children during week 5. But afterwards the amount of late children is significantly higher than the control group.

```{r, warning=FALSE}
xyplot(No.ofLateChildren ~ Week, data = Late_week_groups, groups = week_group, type = c("p", "a"), auto.key = list(corner = c(1,1)), main = "Comparing the number of late children before, during and after the fine")
```

This graph just shows that the lowest number of late children was the period before the fine. During the fine it increased and after the fine was taken away it didn't drop that much. The table below shows the average amount of kids that were picked up late during these different periods of time.

```{r, warning=FALSE}
mean_across_groups_summarization <- Late_week_groups %>%
  filter(Treatment == "Fine") %>%
  group_by(week_group) %>%
  summarise(average = mean(No.ofLateChildren))

pander(mean_across_groups_summarization, caption = "Means of late children before the fine, during the fine and after the fine")
```


## Conclusion
Here we get some suprising results. We see that with a fine the amount of late children that are being picked up actually increases with a fine. I will give a couple of potential reasons. This experiment was done on private daycare places meaning that the people that could afford them did not mind spending the extra money for picking their child up late as they were more well off to begin with. The second reason could be that the parents felt personaly attacked by the fine so they kept their children late in day care out of spite for the facility. Anyways to uncover the true reason behind the increase in the amount of late children with a fine we need to look at other data mabye more specific to the parents.

