---
title: "Recalling Words"
output: 
  html_document:
    theme: cerulean
    code_folding: hide
---

<script type="text/javascript">
 function showhide(id) {
    var e = document.getElementById(id);
    e.style.display = (e.style.display == 'block') ? 'none' : 'block';
 }
</script>

```{r, include=FALSE}
library(mosaic)
library(car)
library(pander)
library(DT) #You may need to run: install.packages("DT") 
library(ggbeeswarm)
```

```{r, eval=FALSE}
# Play the chunk above and this one to get the data into your Console
View(Friendly)
?Friendly
```


<br />

#### Background

Many teachers and other educators are interested in understanding how to best deliver new content to students. In general, they have two choices of how to do this.

1. The Meshed Approach
    * Deliver new content while simultaneously reviewing previously understood content.

2. The Before Approach
    * Deliver new content after fully reviewing previously understood content.

A study was performed to determine whether the *Meshed* or *Before* approaches to delivering content had any positive benefits on memory recall. 

<div style="padding-left:15px;">

##### <a href="javascript:showhide('uniquename')">The Experiment <span style="font-size:8pt;">(click to view)</span></a>


<div id="uniquename" style="display:none;">

Individuals were seated at a computer and shown a list of words. Words appeared on the screen one at a time, for two seconds each, until all words had been shown (40 total). After all words were shown, they were required to perform a few two-digit mathematical additions (like 15 + 25) for 15 seconds to avoid immediate memory recall of the words. They were then asked to write down as many of the 40 words as they could remember. They were given a maximum of 5.3 minutes to recall words.

The process of showing words and recalling words was repeated four times with the same list of words each time (four chances to get it right). The presentation of the first trial was the same for all treatment conditions. However, trials 2, 3, and 4 were slightly different for each treatment condition.

<div style="padding-left:15px;">

The `SFR` group (the control group) stands for Standard Free Recall. In all four trials the same list of 40 words was presented, in a random order each time.

The `Before` group also used the same 40 words during each trial. However, any words that were correctly recalled in a previous trial were presented first, or *before* the words that were not recalled in the last trial. After all the correct words were presented in random order, the non-recalled words were presented in a random order.

The `Meshed` group also used the same 40 words during each trial. However, words that were correctly recalled in a previous trial were alternated with a missed word during the next presentation order. 

</div>

The data records the number of correctly recalled words (out of the 40 possible) from the fourth trial. Results were obtained for 30 students, 10 in each of the three treatment groups: `SFR`, `Before`, and `Meshed`. 

</div>

##### <a href="javascript:showhide('uniquename2')">The Data <span style="font-size:8pt;">(click to view)</span></a>

<div id="uniquename2" style="display:none;">

The results from the study can be found in the `Friendly` data set in R after loading `library(car)`. 

Click the "Code" button to see the data.


```{r, warning=FALSE}
datatable(Friendly, options=list(lengthMenu = c(3,10,30)))
```


</div>
</div>

<br />


<!-- Begin writing your analysis below here. -->

<!-- Note that your goal is to use the Friendly data to show whether or not the Meshed or Before methods have any positive benefit on memory recall. -->


# Questions and Hypotheses
* The question: Is the before and after method for remembering better than just the control?
* The null hypothesis: There is no difference between the effectiveness of standard free recall (control) and the other methods.
* The alternative hypothesis: One of the other methods is better than the standard free recall (control) method.


# Analysis
First, we will perform a qq test to check the normality of each group of data. It looks like our we have some data that isn’t normal from the “before” method and the “meshed” method. It seems like the same people weren’t used for each test of the memory recall methods so we will use and independent samples test. So, to do our analysis on the data the most appropriate test to use is the Wilcox Rank-Sum (Mann-Whitney) Test. I will do three separate Wilcox Rank-Sum tests first, seeing if the “before” method is better than the control. Second, I will see if the “meshed” is better than the controlled. Third, I will see if the “meshed” is better than the “before” method.

### qq test to check the normality of the data:
```{r, warning=FALSE}
qqPlot(correct ~ condition, data = Friendly)

```

###  First Wilcox Rank-Sum test seeing if the “before” method is better than the control
```{r, warning=FALSE}
a <- wilcox.test(Friendly$correct[Friendly$condition == "Before"],Friendly$correct[Friendly$condition == "SFR"] ,mu = 0, alternative = "greater")

pander(a)

```

Using an alpha value of 0.05 we see that we can accept the alternative hypothesis that the "before" method was better than the control because our p value is under 0.05.

### Second Wilcox Rank-Sum test seeing if the “meshed” method is better than the control
```{r, warning=FALSE}
a <- wilcox.test(Friendly$correct[Friendly$condition == "Meshed"],Friendly$correct[Friendly$condition == "SFR"] ,mu = 0, alternative = "greater")

pander(a)

```

It looks like our p-value is just over 0.05 so we have to reject the alternative hypothesis that the "meshed" method is better than the control method. It also seems like we can stop here since we accepted that the "before" method was better than the control.

# Graphical Summary
I will show a box-plot combined with a jitter plot to show the distribution of the data. This will give us the spread of the data and more valueable information than just a boxplot would show especially for so few data points.

```{r, warning=FALSE}
ggplot(data = Friendly) +
  geom_boxplot(mapping = aes(x = condition, y = correct, fill = condition)) +
  geom_quasirandom(mapping = aes(x = condition, y = correct)) +
  labs(title = "Distribution of our data points", subtitle = "the box plots can be missleading with so few data points", x = "memorization style", y = "number of remembered words")
      
         
```

# Interpretation

It seems like there’s a really high 75th percentile for the SFR random control method that is comparable to the other methods but actually looking at the data there are only a few points up there and they’re very spread out compared to the other memorization methods in which more data points are higher up and grouped together. This shows that the other methods look more effective as a memorization technique particularly the “before” method which we proved in the analysis.

# Conclusion
Based off of our analysis and graphical summary with a small limited dataset it seems like the best way to memorize information is to review old content before diving into learning new information. 




